Mapping mutational effects along the evolutionary landscape of HIV envelope

### 2018-01-07 paper/manuscript.tex
tweaks for eLife full submission

\section{Acknowledgments}
We thank Michael Doud and Orr Ashenberg for computer code that formed the basis for some of the analyses.
We thank Andrew Ward for pointing out to us that some of the sites with slower-than-expected rates of evolution are involved in Env's conformational changes upon receptor binding.
We thank Kelly Lee for helpful input about the relative stabilities of the BG505 and BF520 Envs.
We thank the Fred Hutch Genomics Core for performing the Illumina deep sequencing.
This work was supported by the following grants from the NIH: DP1-DA039543 from the NIDA to JO and R01-AI127893 from the NIAID to JDB.
The work was also supported in part by a Collaboration for AIDS Vaccine Discovery Grant (OPP1111923).
The research of JDB is supported in part by a Faculty Scholar Grant from the Howard Hughes Medical Institute and the Simons Foundation.
HKH was supported by a Cell and Molecular Biology Training Grant (T32GM007270) from the NIGMS of the NIH.
ASD was supported by an NSF Graduate Research Fellowship (DGE-1256082).

>>>>

\section{Acknowledgments}
We thank Michael Doud and Orr Ashenberg for computer code that formed the basis for some of the analyses.
We thank Andrew Ward for pointing out to us that some of the sites with slower-than-expected rates of evolution are involved in Env's conformational changes upon receptor binding.
We thank Kelly Lee for helpful input about the relative stabilities of the BG505 and BF520 Envs.
We thank the Fred Hutch Genomics Core for performing the Illumina deep sequencing.
